Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-16 paper.tex
Add acknowledgements and minor change.

    \caption{
        Qualitative comparison of example query images between experiments with
        and without inclusion of the orientaion branch.
        Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
        (upper) to MTML-OSG (below) trained and tested on the VeRi-776.
        AP refers to Average Precision of that query.
    }
    \label{fig:ranks}
%    \vspace{-0.7cm}
\end{figure*}

@@

>>>>

    \caption{
        Qualitative comparison of example query images between experiments with
        and without inclusion of the orientation branch.
        Rank-1 to Rank-10 is shown. Each pair compares MTML-SG
        (upper) to MTML-OSG (below) trained and tested on the VeRi-776.
        AP refers to Average Precision of that query. Correct and
        incorrect identity matches are shown with \textcolor{green}{green}
        and \textcolor{red}{red} borders around images, respectively.
    }
    \label{fig:ranks}
%    \vspace{-0.7cm}
\end{figure*}

@@

This work is partially supported by Vision Semantics Limited and the
Innovate UK Industrial Challenge Project on Developing and Commercialising
Intelligent Video Analytics Solutions for Public Safety (98111-571149).
